# 2020-02-18: Testing

From <https://r-pkgs.org/tests.html>


## Objectives

* Understand why testing is important.
* Learn how to setup testing infrastructure.
* Understand how tests are structured.
* Learn how to run all tests.
* Understand what to test.



## Why testing?

* Discuss



## Set up

```R
usethis::use_testthat()
```

Among other things, `usethis::use_testthat()` attaches testthat in tests/testthat.R

```{r}
library(testthat)
```



## Workflow

* Modify your code or tests.
* Test your package with Ctrl/Cmd + Shift + T or devtools::test().
* Repeat until all tests pass.



## Tests structure

If R/max_minus_min.R contains:

```{r}
max_minus_min <- function(x) {
  max(x) - min(x)
}
```

Then tests/testthat/test-max_minus_min.R may contains:

```{r}
test_that("max_minus_min with simple good input returns expected output", {
  expect_equal(max_minus_min(2:1), 1)
  expect_equal(max_minus_min(2:1), 1)
})
```



## What to test?

> Whenever you are tempted to type something into a print statement or a debugger expression, write it as a test instead. -- Martin Fowler

* Test what should work.

```{r}
test_that("max_minus_min with simple good input returns expected output", {
  expect_equal(max_minus_min(2:1), 1)
  expect_equal(max_minus_min(2:1), 1)
})
```

## What to test?

> A QA engineer walks into a bar. Oders a beer. Orders 0 beers. Orders 9999999 beers. Orders a lizard. Orders -1 beers. Orders a afdelijknesv. -- Bill Sempf (@sempf) on Twitter

* Test what should fail.

```{r}
test_that("max_minus_min with bad input throws an error", {
  expect_error(max_minus_min(letters), "non-numeric argument")
})
```

* Edge cases.

```{r, error=TRUE}
test_that("max_minus_min with edge cases behaves as expected", {
  expect_equal(max_minus_min(NA_integer_), NA_integer_)
  
  # Oh no! I need to modify my code until this test passes
  expect_equal(max_minus_min(c(1, 2, NA)), 1)
})
```



## Questions

1. Do I need a package to test?
1. What are all/common testthat expectations?
1. How can I test that the data my code needs hasn't change?
1. How often should I test?
1. What should I not test?
